Standartox: Standardizing toxicity data

### 2020-04-07 article/tikz/standartox-organigram.tex
update

\node (taxa) [ids, below of = cas, xshift = 0cm, yshift = -2.5cm] {\Large Taxa};

@@

\node (stx-data) [standartox, below of = ecotox-chck, xshift = 3cm, yshift = -2.5cm, align = center] {\Large Standartox\\\Large data set};

>>>>

\node (taxa) [ids, below of = cas, xshift = 0cm, yshift = -2.5cm] {\Large Taxon};

@@

\node (stx-data) [standartox, below of = ecotox-chck, xshift = 3cm, yshift = -2.5cm, align = center] {\Large Standartox\\\Large database};
